Abstract Data Type Inference

### 2015-03-22 patterns.tex
Motivations for many sections.

%!TEX root = draft.tex
\section{Computing ADT Complements}
\label{sec:patterns}

TODO MOTIVATE THIS SECTION; ALSO, RETHINK THE TITLE OF THIS SECTION

@@

TODO MOTIVATE WQO

A \emph{well-quasi-ordering (wqo)} $R$ on a set $X$ is a reflexive, transitive
binary relation on $X$ for which in every infinite sequence $x_0 x_1 \ldots$ of
elements from $X$, there exists indices $i < j$ such that $R(x_i,x_j)$.

@@

>>>>

\section{Computing Finite ADT Representations}
\label{sec:patterns}

In this section we demonstrate that naturally-occurring ADTs can be precisely
represented by finite sets of histories, despite the fact that these ADTs admit
infinite sets of histories. This results is nontrivial, and relies on the
identification of certain algebraic properties of the sets of histories
admitted by ADTs. In particular, we find that these sets of histories are
closed under the removal of certain operations, and that sets of histories
adhere to a well-founded ordering under the relation induced by such removals.

@@

Besides this closure property, the $\preceq$ relation enjoys a certain notion
of well-foundedness (when restricted to certain class of histories): a
\emph{well-quasi-ordering (wqo)} $R$ on a set $X$ is a reflexive, transitive
binary relation on $X$ for which in every infinite sequence $x_0 x_1 \ldots$ of
elements from $X$, there exists indices $i < j$ such that $R(x_i,x_j)$.

@@

\begin{example}
  \label{ex:patterns}
